Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-11-26 man/ecosystems/ms_ecosystems.Rmd
update content

During the last two drought events, resilience metrics for greenness and tree-growth were significantly different between drought events (Table 3). The 2005 drought event reduced greenness and growth more than that of 2012 (Tables S1-S2) but the metrics of resilience generally covaried in the same direction those two years. We obtained significantly higher resilience and resistance values for 2012, the most severe event, than for 2005 in both variables (Tables S1-S2; Figure 6). Thus, recovery values for greenness were higher for 2005 than for the 2012 drought event (Table S1, Figure 6). Recovery showed a contrasting pattern for EVI and tree-growth.

The resilience metrics calculated significantly varied between sites, except for resilience of tree-growth (p = 0.534; Table 3), which was similar among the three sites. The two southern populations showed lower values for recovery than the northern site both for greenness and tree-growth but resistance and resilience values were significantly higher for the southern site (Tables S1-S2).

>>>>

During the last two drought events, resilience metrics for greenness and tree-growth were significantly different between drought events (Table S1). The 2005 drought event reduced greenness and growth more than that of 2012 (Table S2) but the metrics of resilience generally covaried in the same direction those two years. We obtained significantly higher resilience and resistance values for 2012, the most severe event, than for 2005 in both variables (Table S2; Figure 6). Thus, recovery values for greenness were higher for 2005 than for the 2012 drought event. Recovery showed a contrasting pattern for EVI and tree-growth.

The resilience metrics calculated significantly varied between sites, except for resilience of tree-growth (p = 0.534; Table S1), which was similar among the three sites. The two southern populations showed lower values for recovery than the northern site both for greenness and tree-growth but resistance and resilience values were significantly higher for the southern site (Table S2).

### 2019-11-26 man/tables/t_robust_anovas.Rmd
update content

**Table 3.** Robust two-way ANOVAs of the resilience metrics of greenness (EVI) and tree-growth (BAI) for the two drought events (in 2005 and 2012) and site.

>>>>

**Table S1.** Robust two-way ANOVAs of the resilience metrics of greenness (EVI) and tree-growth (BAI) for the two drought events (in 2005 and 2012) and site.
